Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-08-03 document/ms.tex
Continuing on with Issue #33 with a goal of having a shareable draft soon.

\begin{figure*}
	\centering
	\includegraphics[width=0.65\textwidth]{figures/single_Teff_v_order}
	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.  The top panel indicates the location and size of spectral chunks used to derive the values in the bottom panel.  The IGRINS orders also show typical atmospheric transmission (red lines) in the infrared.  Unused spectral chunks are lightened.  The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.}
	\label{fig:SingleTeffvsOrder}
\end{figure*}

@@

Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.  These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.  Assuming the areal coverage fraction of spots was the same or greater during the ESPaDOnS spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.  The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.

@@

Full-spectrum fitting was performed for 43 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.  The MCMC samples had 5000 steps with 40 walkers.  The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range was $\teffa, \teffb \in [2700, 4500]$.  $H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$.  The MCMC chains all appeared to converge after about 1500 steps.

Marginalized distributions were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.  The fit quality was first assessed by examining the consistency of the point estimates across the spectral orders.  The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.  The range for all 43 orders was $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.  Two orders with poor telluric correction ($o=91$ and $94$) had exceptionally large uncertainties on their values for $v_z$ and $\vsini$.

Some orders indicates that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.  These spectral line outlier orders also tend to bias estimates of effective temperature.  These metal lines can also be biased by Zeeman broadening, which would explain the heightened effect size with wavelength.

Finally, the posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.  
\todo{insert results from re-run of H-band spectra here}
Nearly-equal solutions could be explained by vanishingly weak spectral lines in one or the other of the effective temperature ranges, in which case the method offers little constraint on $\teffb$, but improves the fit around $\teffa$.

@@

\input{tables/tbl_order_results.tex}

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
	\caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $f_{\Omega}$, derived independently from full-spectrum fitting to 41 IGRINS orders.  Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=111$) consistent with negligible starspot emission, and others ($o=104, 102, 100$) showing tight constraints on the filling factor of starspots.  The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.  $K-$band orders show lower estimates for the ambient photosphere, though some of these estimates are unreliable due to spectral line outliers}
	\label{fig:TwoTempResults}
\end{figure*}

@@

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/single_Teff_v_order}
	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.  The top panel indicates the location and size of spectral chunks used to derive the values in the bottom panel.  The IGRINS orders also show typical atmospheric transmission (red lines) in the infrared.  Unused spectral chunks are lightened.  The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.}
	\label{fig:SingleTeffvsOrder}
\end{figure}

@@

Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.  These spectra have comparable albeit different $V_{\rm est}$ of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.  Assuming the areal coverage fraction of spots was the same or greater during the ESPaDOnS spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.  The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.

@@

Full-spectrum fitting was performed for 48 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.  The MCMC samples had 5000 steps with 40 walkers.  The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range was $\teffa, \teffb \in [2700, 4500]$.  $H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$.  The MCMC chains all appeared to converge after about 1500 steps.

Marginalized distributions were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.  The fit quality was first assessed by examining the consistency of the point estimates across the spectral orders.  The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.  The range for all 48 orders was $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.  Two orders with poor telluric correction ($o=91$ and $94$) had exceptionally large uncertainties on their values for $v_z$ and $\vsini$.

The posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Appendix Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.

Overplotting models with the observed spectra yielded insights on why some orders failed, and which orders can discriminate between starspots and ambient photospheric lines the best.  Some orders indicate that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.  These spectral line outlier orders also tend to bias estimates of effective temperature.  These metal lines can also be biased by Zeeman broadening, which would explain the heightened effect size with wavelength.

\todo{insert results from re-run of H-band spectra here}
Nearly-equal solutions could be explained by vanishingly weak spectral lines in one or the other of the effective temperature ranges, in which case the method offers little constraint on $\teffb$, but improves the fit around $\teffa$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
	\caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $f_{\Omega}$, derived independently from full-spectrum fitting to 48 IGRINS orders.  Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=111$) consistent with negligible starspot emission, and others ($o=104, 102, 100$) showing tight constraints on the filling factor of starspots.  The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.  $K-$band orders show lower estimates for the ambient photosphere, though some of these estimates are unreliable due to spectral line outliers}
	\label{fig:TwoTempResults}
\end{figure*}

@@

\section{Full table of IGRINS best fits}

Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
\comm{It's not clear if we need this table...}
\input{tables/tbl_order_results.tex}
